FinalManuscript_DISCS_UG

### 2018-10-05 parts/02_relatedliterature.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition

We begin with an overview of image processing, in which we define the image processing operations we are interested in
We first introduce concepts in cryptography and define homomorphic cryptosytems. along with some examples from the literature. Then, we present some concepts in , a suitable application of cryptography, specifically the common image operations used. Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.

\input{parts/02_relatedliterature_01commonimageprocessingoperations}
%facial recognition - theory
\input{parts/02_relatedliterature_02homomorphiccryptosystems}
\input{parts/02_relatedliterature_03partiallyhomomorphic}
\input{parts/02_relatedliterature_04fullyhomomorphic}
%facial recognition - implementation
\input{parts/02_relatedliterature_05previousimplementations}

>>>>

We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on. Then, we define the image processing operations we are interested in implementing in this study and
After establishing our desired image processing operations, introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.

\input{parts/02_relatedliterature_01cryptoimg}
\input{parts/02_relatedliterature_02commonimageprocessingoperations}
%facial recognition - theory
\input{parts/02_relatedliterature_03facialrecognition}
\input{parts/02_relatedliterature_04homomorphiccryptosystems}
\input{parts/02_relatedliterature_05partiallyhomomorphic}
\input{parts/02_relatedliterature_06fullyhomomorphic}
%facial recognition - implementation
\input{parts/02_relatedliterature_07previousimplementations}

### 2018-10-05 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition

\section{Common Image Operations}
In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations. These operations are performed on digital images. We can represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.

\subsection{Intensity Transformation}
To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}. An image negation operation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general form
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical perceived light intensity and digital pixel intensity values. A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

In the \textit{CryptoImg} software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we aim to investigate the overhead required to approximate these functions.

\subsection{Spatial Filtering}
Many common image operations are expressed as \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
\begin{align} \label{eq:spatialfilter}
	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
\end{align}
where $A(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $A$.

@@

There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?

>>>>

\section{Image Processing Operations}
The \textit{CryptoImg} library implemented several
We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.

We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.

\subsection{Intensity Transformations}
An Intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.

The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
An image negation transformation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

A brightness control transformation with parameter $v$ is defined as:
\begin{equation}
    T\left(r,v\right) = r+v
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

In this study we extend the range of intensity transformations to non-linear transformations. Two common non-linear image transformations are the log transformation and power-law transformation~\cite{gonzalez_digital_2008}.

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general formula
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.
A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we investigate methods required to approximate the logarithm and functions.

\subsection{Spatial Filtering}
The \textit{CryptoImg} library also implemented \textit{spatial filters}. Spatial filters are operators which determine output pixels using information from neighboring input pixels. To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
\begin{align} \label{eq:spatialfilter}
	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
\end{align}

@@

There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}

%% TODO: specific list of kernels to use for this study
